SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-07-03 scipy-1.0/covlett.tex
Update scipy-1.0/covlett.tex
Co-Authored-By: Alessandro Pietro Bardelli <apbard@users.noreply.github.com>

We have specifically chosen \emph{Scientific Reports} because
the breadth of acceptable topics matches the breadth of algorithms
our library provides. High-profile manuscripts citing SciPy range
from the biosciences to recent reports on gravitational waves and
black holes. These citations target a website, and we now think
it is well past time that our mature library has a peer-reviewed
journal article describing it.

>>>>

We have specifically chosen \emph{Scientific Reports} because
the breadth of acceptable topics matches the variety of algorithms
our library provides. High-profile manuscripts citing SciPy range
from the biosciences to recent reports on gravitational waves and
black holes. These citations target a website, and we now think
it is well past time that our mature library has a peer-reviewed
journal article describing it.
